Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-19 paper/main.tex
update feature importances table

\begin{table}[]
\begin{tabular}{l|l|l}
Feature Name & Feature Category & Feature Predictive Power \\ \hline
F-Type-C1=unknown & Contextual (Type) & 0.112 \\
F-Type-P=TUPLE & Contextual (Type) & 0.108 \\
F-Stmt-Constr-C2=Return & Contextual (Syntactic) & 0.068 \\
F-Expr-Constr=Paren & Syntactic & 0.059 \\
F-InSlice=0.0 & Slicing & 0.044 \\
F-Type-P=str & Contextual (Type) & 0.036 \\
F-Op-Contr-C3=BinaryAnd & Contextual (Syntactic) & 0.026 \\
F-Type-C2= & Contextual (Type) & 0.025 \\
F-Type-C1=str & Contextual (Type) & 0.023 \\
F-Type-P=float & Contextual (Type) & 0.019 \\
\end{tabular}
\caption{Based on the Top-1 Decision Tree on the full dataset. Feature Predictive Power here is the Gini Importance. TODO: add
better-known measure like ANOVA or ReliefF. TODO: add a couple more features?}
\label{tab:feature-predictive-power}
\end{table}

@@

\begin{figure}
\foreach \method in {single, complete, average}
{
\begin{tikzpicture}
  \begin{axis}[
      xlabel=Threshold,
      ylabel=\# of clusters,
      ytick distance=2,
      title=Linkage: \method
    ]
    \addplot+[mark=none] table[x=threshold, y=python_twenty_cluster_counts_\method, col sep=comma]{cluster_counts.csv};
\end{axis}
\end{tikzpicture}
}
\caption{The number of clusters when clustering a baseline of twenty dissimilar programs from
  Rosetta Code. We give no plot for the baseline of 5000 identical programs, as they were
  consistently placed in just 1 cluster.}
\label{fig:diversity-baseline}
\end{figure}

\begin{figure}
\foreach \method in {single, complete, average}
{
\begin{tikzpicture}
  \begin{axis}[
      xlabel=Threshold,
      ylabel=\# of clusters,
      ytick distance=1000,
      title=Linkage: \method
    ]
    \foreach \language in {ocaml, python}
    {
      \addplot+[mark=none] table[x=threshold, y=\language_cluster_counts_\method, col sep=comma]{cluster_counts.csv};
    }
\legend{OCaml, Python}
\end{axis}
\end{tikzpicture}
}
\caption{Number of clusters when data is clustered by single, complete, and average linkage.
  A linkage tree is built using agglomerative clustering, and the resulting tree is broken up
  into clusters by thresholding the inconsistency coefficient. The inconsistency coefficient
  of a link is its distance, z-scored against other nearby links.}
\label{fig:diversity}
\end{figure}

>>>>

\begin{table}[]
\begin{tabular}{l|l|l}
Feature Name & Feature Category & Feature Predictive Power \\ \hline
F-Size-P & Contextual (Syntactic) & 0.112624 \\
F-Stmt-Constr-C3= & Contextual (Syntactic) & 0.061552 \\
F-Expr-Constr-P=List & Contextual (Syntactic) & 0.054632 \\
F-PythonBlame & Dynamic (Error location) & 0.039189 \\
F-Type=unknown & Dynamic (Type) & 0.037390 \\
F-Type-P=unknown & Contextual (Type) & 0.037330 \\
F-PythonMsg=IndexError & Dynamic (Error message) & 0.032749 \\
F-Size & Syntactic & 0.028203 \\
F-Expr-Constr-P=Dictionary & Contextual (Syntactic) & 0.026663 \\
F-Size-C1 & Contextual (Syntactic) & 0.023662 \\
F-Expr-Constr=Var & Syntactic & 0.020390 \\
F-Type-C1=unknown & Contextual (Type) & 0.019815 \\
\end{tabular}
\caption{Based on the Top-3 Decision Tree on the full dataset. Feature Predictive Power here is the Gini Importance. TODO: add
better-known measure like ANOVA or ReliefF.}
\label{tab:feature-predictive-power}
\end{table}

@@

\begin{figure}
\foreach \method in {single, complete, average}
{
\begin{tikzpicture}
  \begin{axis}[
      xlabel=Threshold,
      ylabel=\# of clusters,
    %   ytick distance=2,
      title=Linkage: \method
    ]
    \addplot+[mark=none] table[x=threshold, y=python_twenty_cluster_counts_\method, col sep=comma]{cluster_counts.csv};
\end{axis}
\end{tikzpicture}
}
\caption{The number of clusters when clustering a baseline of twenty dissimilar programs from
  Rosetta Code. We give no plot for the baseline of 5000 identical programs, as they were
  consistently placed in just 1 cluster.}
\label{fig:diversity-baseline}
\end{figure}

\begin{figure}
\foreach \method in {single, complete, average}
{
\begin{tikzpicture}
  \begin{axis}[
      xlabel=Threshold,
      ylabel=\# of clusters,
    %   ytick distance=1000,
      title=Linkage: \method
    ]
    \foreach \language in {ocaml, python}
    {
      \addplot+[mark=none] table[x=threshold, y=\language_cluster_counts_\method, col sep=comma]{cluster_counts.csv};
    }
\legend{OCaml, Python}
\end{axis}
\end{tikzpicture}
}
\caption{Number of clusters when data is clustered by single, complete, and average linkage.
  A linkage tree is built using agglomerative clustering, and the resulting tree is broken up
  into clusters by thresholding the inconsistency coefficient. The inconsistency coefficient
  of a link is its distance, z-scored against other nearby links.}
\label{fig:diversity}
\end{figure}
